The Spatial and Temporal Domains of Modern Ecology

### 2017-06-28 paper/main.tex
Small text tweak to line 108-9 of final submitted version

For our final analysis of observational domains, we evaluated the differences between the scales represented by the extent and duration dimensions and the scales that ecological observations actually cover. To make this assessment, we log$_{10}$ transformed and then subtracted the values of i) actual extent from extent and ii) actual duration from duration, yielding the magnitude of difference between each pair of dimensions for each observation. We plotted these values (summarized in box plots) against their corresponding actual extent/duration values to evaluate whether these differences vary with scale (Fig. 3). This analysis showed that most (81\%) of the assessed observations had actual extents of $\leq$1 ha, which on average were 4 to nearly 8 orders of magnitude smaller than the primary measure of extent (Fig 3A). These differences declined linearily with actual extent, becoming approximately equal for the 5\% of observations having $\geq$100,000 ha actual extent. The actual duration of 64\% of observations was $<$1 day, which on average was 3 to nearly 9 orders of magnitude shorter than the time span covered by the conventional metric of duration (Fig. 3B). As with extent, the magnitude of difference declined steadily with actual duration, effectively disappearing for the 16\% of observations with $\geq$1 month of actual duration.

>>>>

For our final analysis of observational domains, we evaluated the differences between the scales represented by the extent and duration dimensions and the scales that ecological observations actually cover. To make this assessment, we log$_{10}$ transformed and then subtracted the values of i) actual extent from extent and ii) actual duration from duration, yielding the magnitude of difference between each pair of dimensions for each observation. We plotted these values (summarized in box plots) against their corresponding actual extent/duration values to evaluate whether these differences vary with scale (Fig. 3). This analysis showed that most (81\%) of the assessed observations had actual extents of $\leq$1 ha, which on average were 4 to nearly 8 orders of magnitude smaller than the primary measure of extent (Fig 3A). These differences declined linearily with actual extent, becoming approximately equal for the 5\% of observations having $\geq$100,000 ha actual extent. The actual duration of 64\% of observations was $<$1 day, which on average was 3 to nearly 9 orders of magnitude shorter than the time span covered by the conventional metric of duration (Fig. 3B). As with extent, the average magnitude of difference declined steadily with actual duration, becoming effectively equal for the 16\% of observations with $\geq$1 month of actual duration.
